A Survey of Quantitative Descriptions of Molecular Structure

### 2012-07-24 paper.tex
some more response to reviews

Topological descriptors take into account connectivity along with atom
and bond labels. They consider the molecule as a labeled graph and
characterize it using graph invariants. In addition to graph
invariants, topological descriptors based on information theory such
as entropy have also been defined\cite{Dehmer:2009uq}. An advantage of
these descriptors is that do not require any intensive pre-processing
steps such as 3D coordinate generation and conformational analysis. In
addition, many graph invariants can be rapidly computed for graphs
corresponding to small molecule structures (even though they may be
computationally intractable on much larger graphs). While this class
of descriptors have been used extensively in predictive modeling
applications
\cite{Garcia-Domenech:2008aa,Randic:2001ad,Besalu:2001aa}, a key
drawback is their lack of interpretability. The abstract nature of
many graph invariants and information theoretic descriptors, their use
in predictive models makes it difficult to explain the model in simple
physicochemical terms, though various attempts have been made at
interpretations \cite{Todeschini:1975dq,Stanton:2003aa}.

>>>>

Topological descriptors take into account connectivity along with atom
and bond labels. They consider the molecule as a labeled graph and
characterize it using graph invariants. In addition to graph
invariants, topological descriptors based on information theory such
as entropy have also been defined\cite{Dehmer:2009uq}. An advantage of
these descriptors is that do not require any intensive pre-processing
steps such as 3D coordinate generation and conformational analysis. In
addition, many graph invariants can be rapidly computed for graphs
corresponding to small molecule structures (even though they may be
computationally intractable on much larger graphs). An example of a
topological descriptor is the Wiener index
\cite{Nikolic:2001aa,Wiener:1947aa}. It is simply the sum of the edge
counts in the shortest paths between all pairs of non-hydrogen
atoms. From a physical standpoint, the descriptor characterizes the
branching in a molecular structure. While this class of descriptors
have been used extensively in predictive modeling applications
\cite{Garcia-Domenech:2008aa,Randic:2001ad,Besalu:2001aa} (for
example, the Wiener index described above has been useful in models of
boiling point data), a key drawback is their general lack of
interpretability. The abstract nature of many graph invariants and
information theoretic descriptors, their use in predictive models
makes it difficult to explain the model in simple physicochemical
terms, though various attempts have been made at interpretations
\cite{Todeschini:1975dq,Stanton:2003aa}.
